The \dealii Library, Version 9.7

### 2025-07-30 9.7/paper.tex
Remove trailing whitespaces.
Add subsubsection for Portable::MatrixFree

\todo[inline]{There were several changes in Portable::MatrixFree: support for
multiple components, generalization to fe degree less than n q points 1d,
support for DeviceVector and BlockVector}

>>>>

\subsection{Portable::Matrix-free}
\texttt{Portable::MatrixFree} utilizes \kokkos to provide support for GPUs from
Nvidia, AMD, and Intel. In this release, we have added support for finite
elements with multiple components, i.e vector-values finite elements. We have
also added support for finite elements where the degree is less than the number
of quadrature points in one direction.

We have also introduced two new classes: \texttt{Portable::DeviceVector} and
\texttt{Portable::DeviceBlockVector}. \texttt{Portable::DeviceVector} is an
alias for \texttt{Kokkos::View} that replaces the raw pointer previously used to
access data on the GPU. \texttt{Portable::DeviceBlockVector} extends
\texttt{Portable::DeviceVector} in a manner similar to the way
\texttt{BlockVector} extends \texttt{Vector} on the CPU.

Finally, we have streamlined the interface of the functor invoked by the GPU
kernel. In the past, this interface included a cell index,
\texttt{Portable::MatrixFree::Data}, which includes precomputed data such as
quadrature points, shape functions, and other informations that needed to be
transferred to the GPU, and \texttt{Portable::MatrixFree::SharedData} which
contained scratch memory used for computation. Now, all this information has
been consolidated into a single new structure:
\texttt{Portable::MatrixFree::Data}, greatly simplifying the interface.
